### 2019-12-03 reports/media/loosely_acc.tex
add accelerator internals

\begin{tikzpicture}
  \tikzstyle{PE}=[rounded corners, draw, thick, minimum size=40pt, align=center]
  \tikzstyle{core}=[PE, draw=NavyBlue, fill=NavyBlue!20]
  \tikzstyle{hwacc}=[PE, draw=OliveGreen, fill=OliveGreen!20]
  \tikzstyle{bus}=[double arrow, draw=Orange, fill=Orange!20, thick,
  minimum width=20pt, double arrow head extend=2pt]

@@

  \node (hwacc1) at (3,0.2) [hwacc] {ACC};
  \node (hwacc2) at (5,0.2) [hwacc] {ACC};

>>>>

\begin{tikzpicture}
  \tikzstyle{PE}=[rounded corners, draw, thick, minimum size=40pt, align=center]
  \tikzstyle{core}=[PE, draw=NavyBlue, fill=NavyBlue!20]
  \tikzstyle{hwacc}=[PE, draw=OliveGreen, fill=OliveGreen!20]
  \tikzstyle{bus}=[double arrow, draw=Orange, fill=Orange!20, thick,
  minimum width=20pt, double arrow head extend=2pt]
  \tikzstyle{accint}=[draw=OliveGreen, fill=OliveGreen!10, outer sep=1pt, inner sep=1pt,
  node distance=0.5pt, opacity=0.85]

@@

  \node (hwacc1) at (3,0.2) [hwacc] {ACC};
  \begin{scope}[name=completeacc, local bounding box=accbb, shift={(3, 0.2)}]
    \node (reg0) [accint, minimum width=25pt, xshift=-5pt, minimum height=5pt, font=\tiny] {REG 0};
    \node (reg1) [accint, minimum width=25pt, minimum height=5pt, below=of reg0, font=\tiny] {REG 1};
    \node (reg2) [accint, minimum width=25pt, minimum height=5pt, below=of reg1, font=\tiny] {REG N};
    \node (spm) [accint, minimum height=15pt, minimum width=5pt, align=center,
    right=of reg0.north east, font=\tiny, anchor=north west] {S\\P\\M};
    \node (accpe) [accint, minimum width=10pt, minimum height=10pt, above=of reg0.north west,
    anchor=south west, font=\tiny] {PE};
    \node (accctl) [accint, minimum width=10pt, minimum height=10pt, above=of spm.north east,
    anchor=south east, font=\tiny] {CTL};
  \end{scope}

  \node (hwacc2) at (5,0.2) [hwacc] {ACC};
